---
title: "Reproducible Research in Collaboration"
subtitle: "Writing Academic Texts on GitHub Together"
author: 
  - "Aaron Peikert, Anabel Büchner & Hannes Diemerling"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
repro:
  packages:
    - xaringanthemer
    - svglite
    - qrcode
    - showtext
    - here
    - rcrossref
  files:
    - snippets/signin.Rmd
    - snippets/signup.Rmd
  apt:
    - rsync
---
class: middle, center

```{r setup, include=FALSE}
library(xaringanthemer)
library(svglite)
library(qrcode)
library(showtext)
library(here)
library(rcrossref)
if(FALSE)library(xaringan)


options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=4, fig.retina=3,
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE,
  dev = "svglite"
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
primary_color <- "#024959"
secondary_color <- "#F2D605"
style_duo(
  primary_color = primary_color,
  secondary_color = secondary_color,
  header_font_google = google_font("Didact Gothic", "400", "400i"),
  text_font_google   = google_font("IBM Plex Sans", "400", "400i"),
  text_font_size = "1.5rem",
  )

style_extra_css(css = list(".todo" = list(color = "#17C25B"),
                           ".optional" = list(color = "#05BCE6"),
                           ".large" = list(`font-size` = "130%"),
                           ".small" = list(`font-size` = "80%"),
                           ".tiny" = list(`font-size` = "50%"),
                           ".full" = list(padding = "0px",
                                          margin = "0px",
                                          border = "0px"),
                           ".vertical" = list(`writing-mode` = "vertical-rl",
                                              `text-orientation` = "mixed")),
                )
```

## ~~Why collaboration?~~

<https://github.com/signup>

---
class: center, middle

## Why collaboration?

```{r journal-funs, echo=FALSE, cache=TRUE}
nauthor <- function(issn, limit = 100){
  raw <- rcrossref::cr_journals_(issn = issn, works = TRUE, sort = "published", limit = limit, select = "author")
  vapply(jsonlite::parse_json(raw)$message$items, \(x)length(x$author), 1)
}

table_author <- function(x){
  raw <- table(cut(x, breaks = c(1:10, 1000), label = c(1:9, "10+"), right = FALSE))
  t(as.matrix(raw, col.names = names(t)))
}
```

---
Nr. of authors in the last 100 articles in:

.pull-left[

**Collabra: Psychology**

]

.pull-right[

```{r, echo=FALSE, cache=TRUE, dependson="journal-funs"}
knitr::kable(table_author(nauthor("2474-7394")), , padding = 2)
```

]


--


.pull-left[

**Psychological Science**

]

.pull-right[


```{r, echo=FALSE, cache=TRUE, dependson="journal-funs"}
knitr::kable(table_author(nauthor("1467-9280")), padding = 2)
```

]

--

.pull-left[


**Nature**

]

.pull-right[

```{r, echo=FALSE, cache=TRUE, dependson="journal-funs"}
knitr::kable(table_author(nauthor("1476-4687")), padding = 2)
```

]

---
class: center, middle

## Who could do their research alone?


---
class: center, middle


## Who could do their research without a computer?

---
class: center, middle

# Collaboration is hard

---

# Moving Parts

* code
* data
* software
* results
* text

---
# Collaborators

* you
--

* your future self

--

* collaborators
    * with less expertise
    * with more expertise, but less time

--

* editors
* reviewers
* readers

---
# Contributions

* high level feedback
* to the text (small)
* to the text (extensive)
* to the code
* to the results
* to the data

---
# Channels

* mail
* verbally
* comments in a document
* changes in a document
* changes on a printout
* via a submission portal
* whats app
* ...

---
class: center, middle

> All happy families are alike; each unhappy family is unhappy in its own way.

.right[Leo Tolstoy from Anna Karenina]

---
class: middle

Happy collaborations:

* don't fight with technology, they take advantage of it
* don't engage in edit wars, they have clear responsibilities

--

This is as much as a **technological** challange, as a **sociological** one.


---

Speaking of technology, why can't we use good old:

* Word
* Google Docs / Overleaf
* Google Collab
* Dropbox / Seafile etc.

---

# Word

.pull-left[

## Upside

* everyone can use it
* track changes

]

.pull-right[

## Downside

* only one person at any given time
* no reproducibility

]

---

# Google Doc / Overleaf

.pull-left[

## Upside

* everyone can use it
* many people
* ~~track changes~~

]

.pull-right[

## Downside

* anyone can edit everything, without anyone noticing
* no reproducibility

]

---

# Google Collab

.pull-left[

## Upside

* many people can edit
* track changes via GitHub
* reproducibility

]

.pull-right[

## Downside

* track changes via GitHub

]

---

# Dropbox & Co

.pull-left[

## Upside

* anyone can use it
* reproducibility

]

.pull-right[

## Downside

* only one person at any given time
* anyone can edit everything, without anyone noticing

]

---

# GitHub / GitLab

.pull-left[

## Upside

* reproducibility
* high level of control
* thousands of people can collaborate
* any collaboration workflow is possible

]

.pull-right[

## Downside

* any collaboration workflow is possible
* highly complex

]


---
class: center, middle

# Collaboration is hard

--

# Github is hard

--

# Alternatives are hard

---
class: center, middle

# Learning Goals

---
name: github

## Technological/GitHub

.pull-left[

1. repositories
2. forks
3. issues
4. pull requests

]

---

## Socialogical

1. everything in one place
2. the issue of trust
3. project and task management
4. distributing work

---
template: github

.pull-right[

    1. [aaronpeikert/repro-workshop](https://github.com/aaronpeikert/repro-workshop/)
    2. in a second
    3. 10min on your own
    4. 90-150min in a team

]

---

## Get Active

.left[

1. aaronpeikert.github.io/repro-collab/self-paced

]

```{r, echo=FALSE}
link <- "aaronpeikert.github.io/repro-collab/self-paced"
```

```{r, echo=FALSE, out.width = "30%", out.extra='style="float:center"'}
generate_svg(qr_code(link), here::here("assets/", "qr_slides.svg"), foreground = secondary_color, background = primary_color, show = FALSE)
knitr::include_graphics("assets/qr_slides.svg")
```


